Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Staronified the intro, nahamsayin

​\Section{Introduction}
Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs. The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML). The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code.

The benefits of MDSD have consistently been reported in academia. Many large companies such as Ericsson and Volvo also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

>>>>

​\Section{Introduction}
Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs. The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML). The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code \cite{staron2006adopting}.

The benefits of MDSD have consistently been reported in academia . Many large companies such as Ericsson, Volvo and ABB also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
